### 2014-12-01 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update report

Figure~\ref{fig:PG_Total_HRR} shows the HRR vs. time based on the fires described in Section~\ref{fire}. In this figure, the solid line represents the prescribed HRR that was input into the simulation (based on a prescribed mass flux), and the dashed line represents the HRR that was calculated by FDS based on the ventilation conditions. The vertical dashed lines represent the times at which ventilation occured: front door opening and closing as well as breaking of a front window for emergency escape. See Table~\ref{tab:vents} for a detailed list of the ventilation that occuring during the indcident. The maximum size of the fire specified in this study was selected such that the conditions aligned with observations and fuel loads from the actual fire incident.

\begin{figure}[!ht]
\includegraphics[width=5.5in]{../Figures/PG_Total_9MW_HRR}
\caption[Prescribed and calculated HRR vs. time from the simulation.]
{Comparison of prescribed and calculated HRRs from the simulation. The vertical lines indicate the times at ventilation occurred.}
\label{fig:PG_Total_HRR}
\end{figure}

In Fig.~\ref{fig:PG_Total_HRR}, the prescribed HRR that was input into the simulation is different than the HRR calculated by FDS based on the ventilation conditions. From 0~s to approximately 9~s, the calculated HRR was in agreement with the prescribed HRR because there was an adequate amount of oxygen for all of the fuel to combust.

>>>>

Figure~\ref{fig:PG_Total_HRR} shows the HRR in the structure vs. time based on the fires described in Section~\ref{fire}. In this figure, the solid line represents the prescribed HRR that was input into the simulation (based on a prescribed mass flux), and the dashed line represents the HRR inside the structure that was calculated by FDS based on the ventilation conditions. The vertical dashed lines represent the times at which ventilation occured: front door opening and closing as well as the breaking of a front window for emergency escape. See Table~\ref{tab:vents} for a detailed list of the ventilation that occuring during the indcident. The maximum size of the fire specified in this study was selected such that the conditions aligned with observations and fuel loads from the actual fire incident.

\begin{figure}[!ht]
\includegraphics[width=5.5in]{../Figures/PG_Total_9MW_HRR}
\caption[Interior prescribed and calculated HRR vs. time from the simulation.]
{Comparison of prescribed and calculated interior HRRs from the simulation. The vertical lines indicate the times at ventilation occurred.}
\label{fig:PG_Total_HRR}
\end{figure}

In Fig.~\ref{fig:PG_Total_HRR}, the prescribed HRR that was input into the simulation is different than the HRR calculated by FDS based on the ventilation conditions. From 0~s to approximately 9~s, the calculated HRR was in agreement with the prescribed HRR because there was an adequate amount of oxygen for all of the fuel to combust. The differences in presribed versus predicted HRR is a result of either fuel within the structure accumulating because of a lack of oxygen or combustion occurring exterior to the structure where fuel and oxygen can mix and react. Fig.~\ref{fig:PG_9MW_HRR} shows the total calculated HRR within the computational domain (includes combustion occuring exterior to the structure) compared to the presribed HRR curve.

\begin{figure}[!ht]
\includegraphics[width=5.5in]{../Figures/PG_9MW_HRR}
\caption[Prescribed and calculated HRR vs. time from the simulation.]
{Comparison of total prescribed and calculated HRRs from the simulation. The vertical lines indicate the times at ventilation occurred.}
\label{fig:PG_9MW_HRR}
\end{figure}

0.675 MW
